SpatialEpi

### 2016-07-08 README.Rmd
Started devtools revamp of SpatialEpi.

---
title: "README"
output: html_document
---

SpatialEpi: Methods and Data for Spatial Epidemiology
===========================================
We load the data and convert the coordinate system from latitude/longitude to a 
grid-based system.  
```{r}
require(SpatialEpi)
data(NYleukemia)
map <- NYleukemia$spatial.polygon
centroids <- latlong2grid(NYleukemia$geo[, 2:3])
population <- NYleukemia$data$population
cases <- NYleukemia$data$cases
```

There were 4 census tracts that were completely surrounded by another census tract (an enclave like Lesotho).  We merge them into their surrounding census tracts and modify the population/case counts and SpatialPolygons object accordingly. 
```{r}
remove <- NYleukemia$surrounded
add <- NYleukemia$surrounding
population[add] <- population[add] + population[remove]
population <- population[-remove]
cases[add] <- cases[add] + cases[remove]
cases <- cases[-remove]
centroids <- centroids[-remove, ]
map <- SpatialPolygons(map@polygons[-remove], proj4string=CRS("+proj=longlat"))
```

We plot the incidence of leukemia for each census tract.  
```{r, fig.height=8, fig.width=8}
plotmap(cases/population, map, log=TRUE, nclr=5)
points(grid2latlong(centroids), pch=4)
```

>>>>

---
title: "SpatialEpi"
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.org/rudeboybert/SpatialEpi.svg?branch=master)](https://travis-ci.org/rudeboybert/SpatialEpi)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/SpatialEpi)](http://cran.r-project.org/package=SpatialEpi)

Package of data and methods for spatial epidemiology.

## Installation

Get the released version from CRAN:

```R
install.packages("SpatialEpi")
```

Or the development version from GitHub:

```R
# If you haven't installed devtools yet, do so:
# install.packages("devtools")
devtools::install_github("rudeboybert/SpatialEpi")
```
